### 2014-11-26 stat343/hw7.tex
added homework 2 and 5 tex files

                \smallskip
                Estimated coefficients:
                \FloatBarrier
                \input{hw7/hw7_1_e} 
                \FloatBarrier
                \begin{center}
                    \includegraphics[width=9cm]{hw7/hw7_1_e} 
                \end{center}
        \end{itemize}
    \item[2.]
    \item[4.]
        As I think we had to show on the midterm,
        \begin{align*}
            H&= X(X^TX)^{-1}X^T //
            H&= QR(R^TQ^TQR)^{-1}R^TQ^T //
            H&= QR(R^TR)^{-1}R^TQ^T //
            H&= QRR^{-1}(R^T)^{-1}R^TQ^T //
            H&= QQ^T
        \end{align*}

>>>>

                \smallskip
                Estimated coefficients:
                \FloatBarrier
                \input{hw7/hw7_1_e} 
                \FloatBarrier
                \begin{center}
                    \includegraphics[width=9cm]{hw7/hw7_1_e} 
                \end{center}
        \end{itemize}
    \item[2.]
        \begin{itemize}
            \item[a)]
                After running the model on the untransformed data, we seem to see a substantial improvement from transformation. The log-likelihood for box-cox is maximized right around $\lambda=.25$, with a confidence interval that excluded $1$, so I transformed the data using $.25$. The end result is an improvement in $R^2$ from $.681$ to $.713$.
                \smallskip
                The untransformed linear model:
                \FloatBarrier
                \input{hw7/hw7_2_a}
                \FloatBarrier                
                \begin{center}
                    \includegraphics[width=9cm]{hw7/hw7_2_a} 
                \end{center}
                The transformed linear model:
                \FloatBarrier
                \input{hw7/hw7_2_a_trans}
                \FloatBarrier                
            \item[b)]
        \end{itemize}

    \item[4.]
        As I think we had to show on the midterm,
        \begin{align*}
            H&= X(X^TX)^{-1}X^T \\
            H&= QR(R^TQ^TQR)^{-1}R^TQ^T \\
            H&= QR(R^TR)^{-1}R^TQ^T \\
            H&= QRR^{-1}(R^T)^{-1}R^TQ^T \\
            H&= QQ^T
        \end{align*}
        As was discussed with added variable plots, for an additional variable $X_i$ added to a regression, if $\hat e_{(-i)}$ are the residuals from the regression excluding $X_i$ and $\hat e$ are the residuals from the regression including it,
        \begin{align*}
            \hat e_{(-i)} &= \hat\beta_i (I-H) X_i + \hat e \\ 
            \hat e_{(-i)} &= \hat\beta_i (I-QQ^T) X_i + \hat e \\ 
        \end{align*}
        From simple linear regression, since \(\hat e_{(-i)}\) has mean $0$, it must be the case that \(\hat\beta_i=\frac{\cov((I-QQ^T) X_i,\hat e_{(-i)})}{\var((I-QQ^T) X_i)}\). Plugging this in, we get
        \begin{align*}
            \hat e_{(-i)} &= \frac{\cov((I-QQ^T) X_i,e_{(-i)})}{\var((I-QQ^T) X_i)} (I-QQ^T) X_i + \hat e \\ 
            \hat e &= \hat e_{(-i)} - \frac{\cov\left((I-QQ^T) X_i,\hat e_{(-i)}\right)}{\var\left((I-QQ^T) X_i\right)} (I-QQ^T) X_i \\ 
            \|\hat e\|^2 &= \left\|\hat e_{(-i)} - \frac{\cov\left((I-QQ^T) X_i,\hat e_{(-i)}\right)}{\var\left((I-QQ^T) X_i\right)} (I-QQ^T) X_i \right \|^2 \\
            RSS &= \left\|\hat e_{(-i)} - \frac{\cov\left((I-QQ^T) X_i,\hat e_{(-i)}\right)}{\var\left((I-QQ^T) X_i\right)} (I-QQ^T) X_i \right \|^2
        \end{align*}
        Thus, we can minimize the $RSS$ by minimizing choosing the variable $X_i$ such that the quantity on the right is minimized.
